### 2014-03-12 src/analysis.Rnw
update

o.stats.sel.one <- subset(o.f(stats.one), select=sel.colnames)
r.stats.sel.one <- subset(r.f(stats.one), select=sel.colnames)
stats.rest <- subset(stats.rest, !grepl('^o[.]', operator))
colnames(o.stats.sel.one) <- new.colnames
colnames(r.stats.sel.one) <- new.colnames
@
\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(o.stats.sel.one, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(r.stats.sel.one, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\bigskip
\caption {The one per element selection criteria results.}
\label{tbl:onesel}
\end{table*}

@@

%The values are given in Table~\ref{tbl:onesel}, and its visaulization is in Figure~\ref{fig:onesel}.
% ----------------------------------------------------------------------
% <<oth>>=
% stats.o <- subset(stats.rest, !grepl('^op', operator))
% o.stats.sel.o <- subset(o.f(stats.o), select=sel.colnames)
% r.stats.sel.o <- subset(r.f(stats.o), select=sel.colnames)
% stats.rest <- subset(stats.rest, grepl('^op', operator))
% colnames(o.stats.sel.o) <- new.colnames
% colnames(r.stats.sel.o) <- new.colnames
% @
% 
% \begin{table*}
% \begin{minipage}[h]{0.49\linewidth}
% <<results='asis'>>=
% print(xtable(o.stats.sel.o, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
% @
% \end{minipage}
% \hspace{0.5cm}
% \begin{minipage}[h]{0.49\linewidth}
% <<results='asis'>>=
% print(xtable(r.stats.sel.o, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
% @
% \end{minipage}
% \bigskip
% \caption {Others}
% \label{tbl:osel}
% \end{table*}
% 
% ----------------------------------------------------------------------

@@

\begin{figure*}[t]
<<op.all.3,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
dfd <- subset(df, !(strategy %in% c('op','opsel')) )
ggplot(dfd, aes(sd.reduction, mutant.reduction)) + geom_point(aes(shape=type, color=sqr)) + facet_wrap(~strategy) + theme(axis.text.x = element_text(angle = 90, hjust = 1))
@
\label{fig:fullimgshape}
\end{figure*}
<<opsel>>=
stats.op <- subset(stats.rest, grepl('^(op|TSDL)', operator))
o.stats.sel.op <- subset(o.f(stats.op), select=sel.colnames)
r.stats.sel.op <- subset(r.f(stats.op), select=sel.colnames)
stats.rest <- subset(stats.rest, !grepl('^(op|TSDL)', operator))
colnames(o.stats.sel.op) <- new.colnames
colnames(r.stats.sel.op) <- new.colnames
@

>>>>

o.stats.sel.one <- subset(o.f(stats.one), select=sel.colnames)
r.stats.sel.one <- subset(r.f(stats.one), select=sel.colnames)
stats.rest <- subset(stats.rest, !grepl('^o[.]', operator))
colnames(o.stats.sel.one) <- new.colnames
colnames(r.stats.sel.one) <- new.colnames

o.stats.sel.one$operator  <- gsub('o[.]1x','1/', o.stats.sel.one$operator)
o.stats.sel.one$scope  <- gsub('.*_','', o.stats.sel.one$operator)
o.stats.sel.one$sampling  <- gsub('_.*','', o.stats.sel.one$operator)

r.stats.sel.one$operator  <- gsub('o[.]1x','1/', r.stats.sel.one$operator)
r.stats.sel.one$scope  <- gsub('.*_','', r.stats.sel.one$operator)
r.stats.sel.one$sampling  <- gsub('_.*','', r.stats.sel.one$operator)

@
\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(o.stats.sel.one), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(r.stats.sel.one), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\bigskip
\caption {The one per element selection criteria results.}
\label{tbl:onesel}
\end{table*}

@@

@@

\begin{figure*}[t]
<<op.all.3,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
dfd <- subset(df, !(strategy %in% c('op','opsel')) )
ggplot(dfd, aes(sd.reduction, mutant.reduction)) + geom_point(aes(shape=type, color=sqr)) + facet_wrap(~strategy) + theme(axis.text.x = element_text(angle = 90, hjust = 1))
@
\label{fig:fullimgshape}
\end{figure*}
<<opsel>>=
stats.op <- subset(stats.rest, grepl('^(op|TSDL)', operator))
o.stats.sel.op <- subset(o.f(stats.op), select=sel.colnames)
r.stats.sel.op <- subset(r.f(stats.op), select=sel.colnames)
stats.rest <- subset(stats.rest, !grepl('^(op|TSDL)', operator))
colnames(o.stats.sel.op) <- new.colnames
colnames(r.stats.sel.op) <- new.colnames

@
